### 2023-01-16 output/DiD/tables/balance_table.tex
Added weighted comparisons to balance table

\begin{tabular}{llcccc}
\toprule
 &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & P-Value & Propensity Score Weighted & P-Value \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.009452 & 0.47 \\
 & No cause & 0.11 & -0.03 & 0.03 & -0.025388 & 0.05 \\
 & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.006068 & 0.73 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.122710 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.011622 & 0.47 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.002972 & 0.47 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.028722 & 0.13 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.028645 & 0.01 \\
 & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.058879 & 0.24 \\
 & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.050925 & 0.02 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.681457 & 0.009452 & 0.469633 \\
 & No cause & 0.11 & -0.03 & 0.031417 & -0.025388 & 0.048559 \\
 & Non-payment of rent & 0.72 & -0.01 & 0.764855 & -0.006068 & 0.734137 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.000000 & -0.122710 & 0.000000 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.477297 & 0.011622 & 0.472201 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.365805 & 0.002972 & 0.473092 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.123046 & 0.028722 & 0.130518 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.002114 & 0.028645 & 0.011994 \\
 & Population density (2010) & 9,031.64 & 0.06 & 0.245975 & 0.058879 & 0.235340 \\
 & Portion white (2010) & 0.60 & 0.06 & 0.007126 & 0.050925 & 0.015556 \\
\cline{1-7}
\bottomrule
\end{tabular}
